\problemname{Generators}

%\illustration{0.3}{image.jpg}{CC-BY 2.0 By X on Y}
% Source: URL to image.

% optionally define variables/limits for this problem
\providecommand\maxn{}\renewcommand{\maxn}{10^5}
\providecommand\maxc{}\renewcommand{\maxc}{10^9}

The volcanic island of Fleeland has never had a proper electric net, but finally the administration of the island
have agreed to build the island's power plants and network.

On the island's coast are its $n$ cities. The administration has surveyed the cities and proposed $m$ of them as possible
locations for a power plant, with the $i$th proposal stating that the company can build a plant in city $c_i$ for
cost $a_i$.

These power plants are very modern and a single plant could power the whole island, but the volcano makes building
power lines across the island a dangerous affair. For $1 \leq i < n$, the company can build power lines between
cities $i$ and $i+1$ for a cost of $b_i$, and between cities $n$ and $1$ for a cost of $b_n$.
A city will receive power if it contains a power plant or is connected to a city with a power plant via power
lines.

What is the cheapest way to power all the cities on the island?

\section*{Input}
	\begin{itemize}
		\item One line containing two integers $n$ ($3\leq n \leq \maxn$) and $m$ ($1\leq m \leq n$), the
			number of cities and the number of possible locations for a power plant.
		\item Then follow $m$ lines, the $i$th of which contains $c_i$ ($1 \leq c_i \leq n$) and $a_i$ ($1
			\leq a_i \leq \maxc$), the $i$th possible location for a power plant, and the cost to build it.

		\item Then follows a line containing $n$ integers $b_i$ ($1 \leq b_i \leq \maxc$), the costs of
			building the power lines.
	\end{itemize}
  The values of $c_{1,\ldots,n}$ are unique and given in strictly increasing order.

\section*{Output}
	Output the minimal cost of powering all cities on the island.

