\problemname{Jigsaw}


You have found an old jigsaw puzzle in the attic of your house, left behind by
the previous occupants. Because you like puzzles, you decide to put this one
together. But before you start, you want to know whether this puzzle was left
behind for a reason. Maybe it is incomplete? Maybe the box contains pieces from
multiple puzzles? 

If it looks like a complete puzzle, you also need to know how big your work
surface needs to be. Nothing worse than having to start a jigsaw over because
you started on a small table.

The box does not tell you the dimensions $w \times h$ of the puzzle, but you can
quickly count the three types of pieces in the box:
\begin{itemize}
	\item
		Corner pieces, which touch two of the edges of the puzzle.
	\item
		Edge pieces, which touch one of the edges of the puzzle.
	\item
		Centre pieces, which touch none of the edges of the puzzle.
\end{itemize}

Do these pieces add up to a complete jigsaw puzzle? If so, what was the original
size of the jigsaw puzzle?


\section*{Input}
	\begin{itemize}
		\item
			One line containing three integers $c$, $e$, and $m$
			($0\leq c,e,m\leq10^9$), the number of corner pieces,
			edge pieces, and centre pieces respectively.
	\end{itemize}

\section*{Output}
	If there exist numbers $w$ and $h$ satisfying $w\geq h\geq 2$ such that the original size of
	the jigsaw puzzle could have been $w\times h$, then output a single
	line containing $w$ and $h$.
	Otherwise, output ``\texttt{impossible}''.

	If there are multiple valid solutions, you may output any one of them.
