\problemname{Moderate Pace}

\providecommand\maxn{}
\renewcommand{\maxn}{1000}

An ultra-marathon is a race that takes place over an uncomfortably long distance
and time, typically lasting for five hours or more. You are part of a group of
three ultra-marathon runners looking to place in this year's Great South-to-North
run from Plymouth to Aberdeen.

You have a set number of days until the next race to train. You will all train
together, as training alone can be dangerous. As everyone has their own schedule
in mind for how many kilometres to run per day, this will not be easy, you will
have to compromise.

The fairest option is to look at each day individually, examine the three options
for how far to run, and to take the median one. That is to say, the option taken
for each day should be one that is not be greater or lesser than both of the
other possibilities at the same time.

\section*{Input}
	\begin{itemize}
		\item A line with the integer $n$ ($1\leq n\leq\maxn$), the number of days of training.
		\item A line with $n$ integers $k_{1,\ldots,n}$ ($0\leq k \leq 10^6$), your ideal daily distances.
		\item A line with $n$ integers $a_{1,\ldots,n}$ ($0\leq a \leq 10^6$), your first colleague's ideal daily distances.
		\item A line with $n$ integers $b_{1,\ldots,n}$ ($0\leq b \leq 10^6$), your second colleague's ideal daily distances.
	\end{itemize}

\section*{Output}
  Output a plan for the $n$ days as $n$ integers, where the distance for every day
  corresponds to the median of choices for that day.
